---
title: "Data and Code in the Publications"
author: "X. Vilaysouk"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This page includes the dataset and code used in my publications. There are separate links for differrent articles.


# Article 1 : 
Title: Greenhouse gas emissions from municipal solid waste management in Vientiane, Lao PDR

<div class="col2"> Full citation: Kamrul Islam, __*Xaysackda Vilaysouk*__, Shinsuke Murakami: Integrating remote sensing and life cycle assessment to quantify the environmental impacts of copper-silver-gold mining: A case study from Laos. **Resources, Conservation and Recycling**, 2020 [DOI:/doi.org/10.1016/j.resconrec.2019.104630](https://www.sciencedirect.com/science/article/pii/S0921344919305361) [Download <i class="fas fa-link"></i>] </div>

This is sample
<div class="col2">  
```{r , echo=FALSE}
plot(pressure)
```
</div>
# Article 2 : 

This is sample


# Article 3:

This is sample

```{r , echo=FALSE}
plot(pressure)
```


# Article 4:

This is sample

```{r , echo=FALSE}
plot(pressure)
```



